Binary companions of red clump stars

### 2017-08-04 paper/main.tex
assumptions listed (but not described)

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Hyphenate binary-star when it is an adjective, not when it is a noun!

@@

We make our posterior samplings under the following assumptions:
\begin{description}
\item[foo] whatevs
\item[bar] and more
\end{description}

@@

>>>>

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!

@@

We perform our individual system fits---that is, make our posterior
samplings---under the following assumptions:
\begin{description}
\item[no trinaries] whatevs: No trinaries or beyond. Obviously wrong!
\item[SB1] whatevs: There is no significant light contributed by the secondary.
\item[Kepler] whatevs: No non-gravitational contributions to RV history.
\item[noise model] whatevs: Measurements are unbiased and noise estimates are correct up to jitter; everything Gaussian.
\item[interim prior] We adopt a prior pdf on binary-system parameters
  with the following properties...
\end{description}

@@

Return to our various assumptions and make sure that we discuss them
\emph{by name} here.
